---
title: "Frequency and length for comparison class prior"
output: html_notebook
---

We imagine the utterance "He is tall" is an incomplete utterance, which gets expanded to "He is a tall man" or "He is tall for a man" assuming a noisy channel-style reconstruction.
The prior distribution on comparison classes (say, between "people" and "basketball players"), then, can be imagined as a prior distribution on the two completions ("He is tall relative to other basketball players" vs. "He is tall relative to other people").

We can thus adopt a "production prior" for the comparison class prior, and can estimate the relative cost of these two utterances by their length and log-frequency.

We will use the Google WebGram corpus, accessed [online](http://corpora.linguistik.uni-erlangen.de/demos/cgi-bin/Web1T5/Web1T5_freq.perl)


```{r}
rm(list = ls())
library(ggplot2)
library(tidyr)
library(dplyr)
library(jsonlite)
```

# Google Web Grams


```{r}
sub_categories <- read.csv("../data/webgram_subcat.csv")
super_categories <- read.csv( "../data/webgram_supercat.csv")
```


```{r}
bind_rows(sub_categories %>% select(X, web.gram.freq) %>% mutate(category = "sub"),
          super_categories %>% select(X, web.gram.freq) %>% mutate(category = "super")) %>%
  rename(cat = X) %>%
  mutate(logfreq = log(web.gram.freq),
         cat = factor(cat, levels = cat[order(logfreq)])) %>%
  ggplot(., aes( x = cat, y = logfreq, fill = category))+
  geom_bar(stat = 'identity', position = position_dodge())+
  coord_flip()
```


 For purposes of the model, we average over a number of similar phrases
 
```{r}
d <- read.csv("../data/class-elicitation-full-trials.csv")

df.freq <- bind_rows(
  sub_categories %>% 
    select(X, web.gram.freq),
  super_categories %>% 
    select(X, web.gram.freq)
) %>% drop_na() %>% spread(X, web.gram.freq)

levels(factor(d$sub_category))
levels(factor(d$super_category))

df.freq.long <- data.frame(
  cat = c(
    "grape","apple","watermelon", "produce",
    "gymnast","soccer player","basketball player","people",
    "bottle opener", "toaster", "dishwasher", "kitchen appliances",
    "day in Winter", "day in Fall", "day in Summer", "days of the year",
    "video of the cute animal", "music video", "movie", "things you watch online"
  ),
  category = c(
    "sub", "sub","sub","super",
    "sub", "sub","sub","super",
    "sub", "sub","sub","super",
    "sub", "sub","sub","super",
    "sub", "sub","sub","super"
  ),
  degree = c(
    "weight","weight","weight","weight",
    "height","height","height","height",
    "price","price","price","price",
    "temperature","temperature","temperature","temperature",
    "duration","duration","duration","duration"
  ),
  freq = c(
    df.freq$grapes, df.freq$apples, df.freq$watermelons, df.freq$`fruits and vegetables`,
    df.freq$gymnasts, df.freq$`soccer players`, df.freq$`basketball players`, df.freq$people,
    df.freq$`bottle openers`, df.freq$toasters, df.freq$`dishwashing machines`, df.freq$`kitchen appliances`,
    (df.freq$`days in Winter` + df.freq$`days of Winter` + df.freq$`Winter days`)/3, 
    (df.freq$`days in Fall` + df.freq$`days of Fall` + df.freq$`Fall days`)/3,
    (df.freq$`days in Summer` + df.freq$`days of Summer` + df.freq$`Summer days`)/3, 
    (df.freq$`days in the year` + df.freq$`days of the year`)/2,
    (df.freq$`videos of animals` + df.freq$`animal videos`)/2,
    df.freq$`music videos`, df.freq$movies, 
    (df.freq$`online videos` + df.freq$`online media`)/2
  )
)
```


```{r}
df.freq.long  %>% 
  mutate(logfreq = log(freq),
         cat = factor(cat, levels = cat[order(logfreq)])) %>% 
  ggplot(., aes( x = cat, y = logfreq, fill = category))+
  geom_bar(stat = 'identity', position = position_dodge())+
  coord_flip()
```


```{r}

df.freq.long  %>% 
  mutate(logfreq = log(freq),
         cat = factor(cat, levels = cat[order(logfreq)])) %>% 
  select(cat, logfreq) %>% spread(cat, logfreq) %>%
  toJSON(., pretty = T)
```

