---
title: "RSA Model understanding"
output: html_notebook
---

```{r}
library(rwebppl)
library(jsonlite)
library(ggthemes)
library(tidyr)
library(dplyr)
library(ggplot2)
```

```{r utils}
utils <- 'var round = function(x){
  return Math.round(x*10)/10
}

var distProbs = function(dist, supp) {
  return map(function(s) {
    return Math.exp(dist.score(s))
  }, supp)
}

var KL = function(p, q, supp) {
  var P = distProbs(p, supp), Q = distProbs(q, supp);
  var diverge = function(xp,xq) {
    return xp == 0 ? 0 : (xp * Math.log(xp / xq) );
  };
  return sum(map2(diverge,P,Q));
};
'
```


```{r language}
language <- '

var thresholdBins ={
  positive: map(function(x){
    return  x - (1/(binParam*2));
  }, sort(statePrior.super.support())),
  negative: map(function(x){
    return  x + (1/(binParam*2));
  }, sort(statePrior.super.support()))
};

var thresholdPrior = cache(function(form){
  return Infer({
    model: function() { return uniformDraw(thresholdBins[form]) }
  });
});


var utterances = {
  positive: ["positive_Adjective",
             "positive_sub",
             "positive_super"],
  negative: ["negative_Adjective",
             "negative_sub",
             "negative_super"]
};


var utterancePrior = cache(function(form){
  return Infer({
    model: function() {
      return categorical({
        vs: utterances[form],
        ps: [1,1,1]
      })
    }
  })
});

var meaning = function(utterance, state, threshold) {
  state > threshold ? flip(1-Number.EPSILON) : flip(Number.EPSILON)
}


// var meaning = function(utterance, state, threshold) {
//   utterance == "positive" ? state > threshold ? flip(0.9999) : flip(0.0001) :
//   utterance == "negative" ? state < threshold ? flip(0.9999) : flip(0.0001) :
//   true
// }

// var meaning = function(utterance, state, threshold) {
//   utterance == "positive" ? state > threshold :
//   utterance == "negative" ? state < threshold :
//   true
// }
'
```


```{r prior}
prior <- '
var binParam = 5;

// var stateParams = {
//   sub: paramsFromR.priorParams.sub[0],
//   super: paramsFromR.priorParams.super[0]
// };
var stateParams = {
    sub: {mu: -1, sigma: 1},
    super: {mu: 0, sigma: 1}
}

var stateVals = map(
  round,
  _.range(stateParams.super.mu - 2 * stateParams.super.sigma,
          stateParams.super.mu + 2 * stateParams.super.sigma,
          stateParams.super.sigma/binParam)
);

var stateProbs = {
  sub: map(function(s){
    Math.exp(Gaussian(stateParams.sub).score(s))+
    Number.EPSILON
  }, stateVals),
  super: map(function(s){
    Math.exp(Gaussian(stateParams.super).score(s))+
    Number.EPSILON
  }, stateVals)
};

var statePrior = {
  sub: Infer({
    model: function(){ return categorical({vs: stateVals, ps: stateProbs.sub}) }
  }),
  super: Infer({
    model: function(){ return categorical({ vs: stateVals, ps: stateProbs.super}) }
  })
};
'
```


```{r}
rsa <- '
// webppl ccrsa.wppl --require adjectiveRSA
var classPrior = Infer({
  model: function(){return uniformDraw(["sub", "super"])}
});

var alphas = {s1: 3, s2: 1};

var literalListener = cache(function(u, threshold, comparisonClass) {
  Infer({model: function(){
    var cc = u.split("_")[1] == "Adjective" ?  comparisonClass :
              u.split("_")[1] == "silence" ?  comparisonClass :
              u.split("_")[1]
    var utterance = u.split("_")[0]
    var state = sample(statePrior[cc]);
    var m = meaning(utterance, state, threshold);
    condition(m);
    return state;
  }})
}, 10000)


var speaker1 = cache(function(state, threshold, comparisonClass, form) {
  Infer({model: function(){
    var utterance = sample(utterancePrior(form))
    var L0 = literalListener(utterance, threshold, comparisonClass)
    factor( alphas.s1 * L0.score(state) )
    return utterance
  }})
}, 10000)

var pragmaticListener = function(form) {
  Infer({model: function(){
    var utterance = form + "_Adjective";
    var comparisonClass = sample(classPrior);
    // var comparisonClass = "super"
    var state = sample(statePrior["sub"]);
    var threshold = sample(thresholdPrior(form));
    var S1 = speaker1(state, threshold, comparisonClass, form);
    observe(S1, utterance);
    return comparisonClass
  }})
}

// pragmaticListener("positive")

// expectation(statePrior["sub"])
// var s = 0
// display("state = " + s)
// var t = thresholdBins.positive[5]
// display("threshold = " + t)
// var c = "super"
_.flatten(_.flatten(
map(function(c){
  map(function(t){
    map(function(s){
        var speakProbs = speaker1(s,t, c, "positive")
       return {  "c": c,
          s:s, 
          t:t, 
          "subUtt": Math.exp(speakProbs.score("positive_sub")),
          "superUtt": Math.exp(speakProbs.score("positive_super")),
          "ambiguous": Math.exp(speakProbs.score("positive_Adjective"))
        }
    }, stateVals)
  }, thresholdBins.positive)
}, ["super","sub"])
))
'
```

```{r}
rs.wp <- webppl(paste(utils, prior, language, rsa, sep = '\n'))

rs.tidy <- rs.wp %>%
  gather(utt, prob, superUtt, subUtt, ambiguous)
```

```{r fig.width = 16, fig.height = 3.5}
ggplot(rs.tidy, aes( x = s, y = prob, color = utt))+
  geom_line()+
  scale_color_solarized()+
  facet_grid(c~t)
```
```{r }
ggplot(rs.tidy %>% filter(c == "super", utt == "subUtt"), aes( x = s, y = prob, color = t, group = t ))+
  ylab("Sub utterance probability")+
  geom_line()
```

Explaining speaker production probabilities for sub: N(-1,1) and super N(0, 1) [same variance, sub has lower mean]. Let's call these LOW and HIGH

- *Comparison class fixed to "HIGH"*
  - When threshold is very low, and the state is low, you say the *LOW* (because it is more likely to be true of the subclass, because it has lower mean)
    - As the state increases, more likely to say *HIGH* or *ambiguous* (since class = "super", *HIGH* and *ambiguous* have the same effect)
  - As the threshold increases, speaker more likely to say *LOW* for higher states than before. 
    - This is because the utterance becomes more informative for the LOW distribution. This trades off with the prior probability of the state under the LOW distribution and the rising informativity under the HIGH distribution.




```{r}
speaker.subUttThreshold <- rs.wp %>%
  filter(subUtt <0.25) %>%
  group_by(t) %>%
  summarize(uttThreshold = max(s))

ggplot(speaker.subUttThreshold, aes( x = t, y = uttThreshold))+
  geom_point()
```

