---
title: "Comparison class models (RSA + BDA)"
output: html_notebook
---

# Empirical data

```{r}
library(langcog)
library(tidyr)
library(dplyr)
library(data.table)
library(coda)
library(knitr)
library(ggthemes)
theme_set(theme_minimal(9))
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

Data analysis for Class Elicitation experiment

Analyzed in terms of proportion *superordinate* responses

```{r}
data.path <-  "../data/"

d.catch <- read.csv(paste(data.path, "class-elicitation-full-catch_trials.csv", sep = ""))

d.catch <- d.catch %>% 
  mutate(pass = response == "relative to other buildings") %>%
  select(workerid, pass)

d <- read.csv(paste(data.path, "class-elicitation-full-trials.csv", sep = ""))
d.tidy <- left_join(d, d.catch) %>%
  filter(pass) %>%
  mutate(superResponse = ifelse(paraphrase == "super", 1, 0)) 

ce.summary <- d.tidy %>%
  group_by(strength, target, degree, adjective, form, sub_category, super_category) %>%
  multi_boot_standard(column = "superResponse")
```

Data analysis for Vague Speaker experiment

```{r}
project.name <- "vague-prior-elicitation-1"

d.catch <- read.csv(paste(data.path, project.name, "-catch_trials.csv", sep = ""))
d.catch <- d.catch %>% 
  mutate(pass = response == "Yes")

d <- read.csv(paste(data.path, project.name, "-trials.csv", sep = ""))

vs.summary <- left_join(d, d.catch %>% select(workerid, pass)) %>%
  filter(pass) %>%
  group_by(strength, target, degree, adjective, 
           form, sub_category, super_category) %>%
  multi_boot_standard(column = "response")

```

## Model results
# Models


### FBT models


```{r load_model_results, cache = T}
load("../models/results/fbt-L1-explAlt-noSilence-empiricalCC-disc3-mcmc50000_burn25000_2chain.RData")

m.samp.tidy <-left_join(
  m.samp %>% filter(param == "prior"),
  d %>% select(degree, sub_category, strength) %>% unique() %>%
  rename(cat = sub_category)
) %>% 
  mutate(strength = factor(strength, levels = c(1,2,3),
                           labels = c("low","medium","high")))



m.freq.summary <- m.samp %>% filter(param == "frequency") %>%
  group_by(param) %>%
  summarize( MAP = estimate_mode(val),
             cred_upper = hdi_upper(val),
             cred_lower = hdi_lower(val) )

m.pp <- m.samp %>% 
  filter(param %in% c("superCC", "superSpeaker")) %>%
  group_by(param, cat,form) %>%
  summarize( MAP = estimate_mode(val),
             cred_upper = hdi_upper(val),
             cred_lower = hdi_lower(val) )
```


Speaker optimality parameters

```{r}
m.samp %>% filter(cat %in% c("speakerOptimality_s1", "speakerOptimality_s2")) %>%
  separate(cat, into = c("cat", "speaker")) %>%
  ggplot(., aes(x = val))+
  geom_histogram()+
  facet_wrap(~ param  + speaker, scales = 'free')
```

Other parameters

```{r}
m.samp %>% 
  filter(cat == "beta") %>%
  ggplot(., aes(x = val))+
  geom_histogram()+
  facet_wrap(~ cat + param, scales = 'free')
```


Prior parameters

```{r}
m.samp %>% filter(param %in% c("mu", "sigma")) %>%
  filter(cat != "") %>%
  ggplot(., aes(x = val))+
  geom_histogram()+
  facet_grid(cat ~ param, scales = 'free')+
    theme_bw()+
  theme(strip.text.y = element_text(angle = 0))
```


```{r}
m.samp %>% filter(param %in% c("mu", "sigma")) %>%
  filter(cat != "") %>%
  group_by(cat, param) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val)) %>%
  kable()
```



What do the priors look like?

```{r}


ggplot(m.samp.tidy %>% mutate(experiment = "Degree \n priors"), 
                aes(x = val, y = ..scaled.., 
                 fill = strength, lty = strength))+
  geom_density(adjust = 2, size = 0.8, alpha = 0.8)+
  scale_fill_manual(values = c("#ffeda0","#feb24c","#f03b20"))+
  facet_grid(experiment~degree, scales = 'fixed')+
  xlim(-3, 3)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab("Degree value")+
  ylab("Prior density")+
  theme(strip.text.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"))
```


Posterior predictives

```{r}
md.pp <- left_join(
  bind_rows(vs.summary %>% 
             mutate(expt = "superSpeaker"),
           ce.summary %>%
             mutate(expt = "superCC")) %>% 
             ungroup() %>%
             rename(cat = sub_category),
  m.pp %>% rename(expt = param))

ggplot(md.pp, aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
                  y = mean, ymin = ci_lower, ymax = ci_upper,
                  shape = form, color = degree))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_errorbar()+
  geom_errorbarh()+
  geom_point()+
  facet_wrap(~expt)+
  coord_fixed(ratio = 1)+
  xlim(0, 1)+
  ylim(0, 1)

print(paste("ccRSA model & cc inference task r^2= ", with(md.pp %>%
       filter(expt == "superCC"), cor(MAP, mean))^2, sep = ""))

print(paste("adjective s2 & vs task r^2= ", with(md.pp %>%
       filter(expt == "superSpeaker"), cor(MAP, mean))^2))
```
### Comparison class inference task

```{r}
md.pp.long <- bind_rows(
  md.pp %>% 
    select(-mean, -ci_lower, -ci_upper) %>%
    rename(mean = MAP, ci_lower = cred_lower, ci_upper = cred_upper) %>%
    mutate(src = "model"),
  md.pp %>%
    select(-MAP, -cred_lower, -cred_upper) %>%
    mutate(src = "human")
)

md.pp.long %>%
  ungroup() %>%
  filter(expt == "superCC") %>%
  mutate(cat = factor(cat, levels = cat[order(strength)])) %>%
  ggplot(., 
         aes( x = cat, 
              y = mean, ymin = ci_lower, ymax = ci_upper, 
              group = form, fill = form ) )+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  facet_grid(src~degree, scales = 'free')+#, nrow = 1)+
  ylim(0, 1) + 
  theme(axis.text.x = element_text(angle = 90) )
```

### Adjective speaker inference task

```{r}
md.pp.long %>%
  ungroup() %>%
  filter(expt == "superSpeaker") %>%
  mutate(cat = factor(cat, levels = cat[order(strength)])) %>%
  ggplot(., 
         aes( x = cat, 
              y = mean, ymin = ci_lower, ymax = ci_upper, 
              group = form, fill = form ) )+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  facet_grid(src~degree, scales = 'free')+#, nrow = 1)+
  ylim(0, 1) + 
  theme(axis.text.x = element_text(angle = 90) )
```

